### 2022-06-28 input/appendices.tex
almost 20p
major changes everywhere

\section{Table of notations}
\label{appendix:notations}

Table~\ref{table:notations} summarizes the notations used throughout
this paper. For the sake of clarity, we divide them into three
categories: network, \process, and message.

\input{input/tablenotations.tex}

\section{Proof of Theorem~\ref{theo:fb}}
\label{appendix:fb}

\begin{proof}
  Whenever a \process~$s$ becomes a source, it broadcasts hence
  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
  its set of received messages, it acknowledges that it belongs to its
  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
  \noindent Such a source forwards its notification to its neighbors.
  Every neighbor eventually receives its notification since
  communication links are reliable. Whatever the order of received
  messages $R_x$ at neighboring \process~$x$, total order ensures that
  it delivers notifications $\alpha_s^{d}$ when
  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
  this case.
  \noindent Among these neighbors, at least those that fulfill the
  latest condition forward their respective notification.  By
  transitivity, the message originating from $s$ reaches all
  \processes that belong to $P_s$ at least through their respective
  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
  quiescent, \ie no \process becomes source anymore, every \process
  eventually acknowledges the partition it belongs to, \ie \processes
  eventually reach consistent partitioning together. In addition, the
  protocol terminates: a \process never delivers hence forwards a
  message after it received, delivered, and forwarded the message of
  its closest source from its lightest path.
\end{proof}

\section{Proof of Theorem~\ref{theo:fbfsdcp}}
\label{appendix:fbfsdcp}

\begin{proof}
  Detection triggers forwarding of staleness downstream which
  completes the case study of Lemma~\ref{lem:detector} by ensuring
  that, when a source broadcasts its staleness notification, all
  \processes that belong to its partition eventually deliver such a
  staleness notification. All downstream bordering \processes also
  eventually receive such a staleness notification and echo back their
  best delivered message. This triggers another competition as in
  Theorem~\ref{theo:fb} for the \processes that delivered the
  staleness notification.
\end{proof}

%% \section{Related work summary}

%% Table~\ref{table:relatedwork} provides a summary of state-of-the-art
%% approaches along with the reason they fail to enable quick content
%% indexing in large scale dynamic systems.

%% \input{input/tablerelatedwork.tex}

>>>>

\section{Table of notations}
\label{appendix:notations}
\input{input/tablenotations.tex}

%% Table~\ref{table:notations} summarizes the notations used throughout
%% this paper. For the sake of clarity, we divide them into three
%% categories: network, \process, and message.

% \section{Appendix: Proofs of Theorem~\ref{theo:fb} and Theorem~\ref{theo:fbfsdcp}}
% \label{appendix:fb}

%%\section{Proof of Theorem~\ref{theo:fbfsdcp}}
%% \label{appendix:fbfsdcp}

### 2022-06-28 input/experiments.tex
meow
major changes everywhere

\subsection{Scalability and trade-off}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by highlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\subsection{Traffic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in dynamic
  inter-autonomous systems.

@@

\begin{asparadesc}
  \item[Overall,] these experiments highlight the scalability of \NAME
    and \NAMEC in dynamic networks such as Edge infrastructures. Next
    Section reviews state-of-the-art approaches that can index content
    in geo-distributed infrastructures.
\end{asparadesc}

>>>>

\subsection{Scalability and trade-off of \NAME}
\begin{asparadesc}
%% \item [Objective:] Confirm the scalability of \NAME by highlighting the
%%   trade-off between the current partitioning of the system and the
%%   protocol's overhead in terms of generated traffic and termination
%%   time.

@@

\subsection{Traffic containment in dynamic inter-autonomous systems}
%% \item [Objective:] Confirm that \NAME locks down the traffic of
%%   decentralized content indexing in dynamic
%%   inter-autonomous systems.

@@

\begin{asparadesc}
\item[Overall,] these experiments highlight the scalability of \NAME
  %and \NAMEC
  in dynamic networks such as Edge infrastructures. Next
  Section reviews state-of-the-art approaches that can index content
  in geo-distributed infrastructures.
\end{asparadesc}

### 2022-06-28 input/figsimplerproblem.tex
meow
lowering page number, still long way to go 23 over 20
major changes everywhere

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
     while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}$\alpha_c^3$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:problemE}$\delta_c$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:problemF}$a$ and $b$ do not belong to any partition but
      $c$ stays forever in a stale one: $P_a$.]
             {\input{input/figsimplerproblemF.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, the
    naive propagation of $\alpha$ and $\delta$ messages may be
    insufficient to guarantee consistent partitioning. If $c$ had
    children, they would stay in the wrong partition too.}
\end{figure*}

>>>>

  \newcommand\X{41pt}
  \newcommand\Y{-40pt}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}$a$ and $c$ delete their partition while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}$a$ receives + delivers $\alpha_c^3$.]
    %$\alpha_c^3$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:problemE}$a$ receives + delivers $\delta_c$.]
    %$\delta_c$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
             {\input{input/figsimplerproblemF.tex}}
  \end{center}
  \caption{\label{fig:problem}% Even in the simplest scenarios,
    The naive propagation of messages is
    insufficient to guarantee consistent partitioning. If $c$ had
    children, they would stay in the wrong partition too.}
\end{figure*}

### 2022-06-28 input/introduction.tex
20p
major changes everywhere

\input{input/figpartitionintuition.tex} %% positioning

Such approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring,doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face slower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

\item [$\bullet$] We evaluate \NAME through simulations using
  PeerSim~\cite{montresor2009peersim}. Results empirically show that
  \begin{inparaenum}[(i)]
  \item \NAME manages to quickly disseminate messages to the subset of
    relevant \processes;
  \item \NAME's overhead decreases when the number of partitions
    increases;
  \item \NAME does not generate traffic in quiescent systems; and
  \item \NAME enables consistent partitioning even in networks subject
    to physical partitioning.
  \end{inparaenum}
\end{asparadesc}

>>>>

Such approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring,doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple %replica
hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face slower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

\item [$\bullet$] We evaluate \NAME through simulations using
  PeerSim~\cite{montresor2009peersim}. Results empirically show that
  \begin{inparaenum}[(i)]
  \item \NAME manages to quickly disseminate messages to the subset of
    relevant \processes;
  \item \NAME's overhead decreases when the number of partitions
    increases;
  \item \NAME does not generate traffic in quiescent systems; and
  \item \NAME operates even in networks subject
    to physical partitioning.
  \end{inparaenum}
\end{asparadesc}

### 2022-06-28 input/proposal.tex
20p
major changes everywhere

@@

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash. % at any time. % For convenience, Appendix~\ref{appendix:notations}
% summarizes the notations used throughout the paper.

@@

We use scoped broadcast to efficiently modify the state of each
\process depending on the partitions that exist in the system.

@@

\begin{proof}
  Proof in Appendix~\ref{appendix:fb}.
%%   Whenever a \process~$s$ becomes a source, it broadcasts hence
%%   delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
%%   its set of received messages, it acknowledges that it belongs to its
%%   own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
%%   it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
%%   \noindent Such a source forwards its notification to its neighbors.
%%   Every neighbor eventually receives its notification since
%%   communication links are reliable. Whatever the order of received
%%   messages $R_x$ at neighboring \process~$x$, total order ensures that
%%   it delivers notifications $\alpha_s^{d}$ when
%%   $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
%%   is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
%%   this case.
%%   \noindent Among these neighbors, at least those that fulfill the
%%   latest condition forward their respective notification.  By
%%   transitivity, the message originating from $s$ reaches all
%%   \processes that belong to $P_s$ at least through their respective
%%   lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
%%     |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
%%     d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
%%   quiescent, \ie no \process becomes source anymore, every \process
%%   eventually acknowledges the partition it belongs to, \ie \processes
%%   eventually reach consistent partitioning together. In addition, the
%%   protocol terminates: a \process never delivers hence forwards a
%%   message after it received, delivered, and forwarded the message of
%%   its closest source from its lightest path.
\end{proof}

@@

\input{input/figsimplerproblem.tex} %% positioning

@@

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that its preceding
\texttt{Add} operation becomes obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications of staleness $\delta_s$. We
focus on the last delivery of each \process, since the best is also
the last, as highlighted by Algorithm~\ref{algo:add}.

@@

\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
    \centernot\implies \textup{DCP}$] Forwarding best up-to-date
  and staleness, and echoing is not sufficient to guarantee
  dynamic consistent partitioning.
\end{lemma}

\begin{proof}
Stale control information (see Definition~\ref{def:lwo}) may impair
the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It echoes back $\alpha_c^3$ to $a$. In Figures~\ref{fig:problemD}
and \ref{fig:problemE}, $a$ and $b$ handle transiting
notifications. Finally, Figure~\ref{fig:problemF} shows that
eventually, $c$ stays in the deleted partition $P_a$ for not having
received $\delta_a$ that $b$ blocked earlier. The system does not
reach consistent partitioning. \end{proof}

@@

\begin{proof}
  Proof in Appendix~\ref{appendix:fbfsdcp}.
%%   Detection triggers forwarding of staleness downstream which
%%   completes the case study of Lemma~\ref{lem:detector} by ensuring
%%   that, when a source broadcasts its staleness notification, all
%%   \processes that belong to its partition eventually deliver such a
%%   staleness notification. All downstream bordering \processes also
%%   eventually receive such a staleness notification and echo back their
%%   best delivered message. This triggers another competition as in
%%   Theorem~\ref{theo:fb} for the \processes that delivered the
%%   staleness notification.
\end{proof}

@@

\begin{algorithm}[t]
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

By reusing \NAME's default behavior of echos and downstream staleness,
Algorithm~\ref{algo:edges} enables dynamic consistent partitioning
even in dynamic networks subject to physical partitioning where
\processes can join, leave, or crash at any time. Adding a \process is
equivalent to add as many edges as necessary. Since adding an edge may
improve shortest paths, the protocol triggers a competition using
echos of Definition~\ref{def:fbplus}.  Removing a \process is
equivalent to removing all its edges. Removing an edge between two
\processes may invalidate the shortest path of one of involved
\processes plus downstream \processes, or impair the propagation of
staleness notifications. Therefore, the protocol reuses its detectors
of Lemma~\ref{lem:detector} to remove irrelevant messages from the
system.

>>>>

\begin{table}
  \caption{\label{table:notations}Notation table.}
  \input{input/tablenotations.tex}
\end{table}

@@

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash. % at any time.
For convenience, Table~\ref{table:notations}
summarizes the notations used throughout the paper.

@@

We use scoped broadcast to efficiently modify the state of each
\process depending on the partitions that exist in the system to reach consistent partitioning.

@@

\begin{proof}
  \input{input/prooftheoremfb}
  % Proof in Appendix~\ref{appendix:fb}.
\end{proof}

@@

@@

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that its preceding
\texttt{Add} operation becomes obsolete. % As consequence,
Their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications of staleness $\delta_s$. We
focus on the last delivery of each \process, since the best is also
the last, as highlighted by Algorithm~\ref{algo:add}.

@@

\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
  staleness, and echoes is not sufficient to guarantee dynamic
  consistent partitioning.
\end{lemma}

\begin{proof}
Stale control information (see Definition~\ref{def:lwo}) may impair
the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links where \processes
receive the messages in the order of their sending. % ($s_{pq}(m)
%\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$).
In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It echoes back $\alpha_c^3$ to $a$. In Figures~\ref{fig:problemD}
and \ref{fig:problemE}, $a$ and $b$ handle transiting
notifications. Finally, Figure~\ref{fig:problemF} shows that
eventually, $c$ stays in the deleted partition $P_a$ for not having
received $\delta_a$ that $b$ blocked earlier. The system does not
reach consistent partitioning. \end{proof}

\input{input/figsimplerproblem.tex}

@@

\begin{proof}
  \input{input/prooftheoremfbfsdcp}
\end{proof}

@@

%% \begin{algorithm}[t]
%%   \input{input/algoedges.tex}
%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
%% \end{algorithm}

By reusing \NAME's default behavior of echos and downstream staleness,
Algorithm~\ref{algo:ascast} also enables dynamic consistent partitioning
even in dynamic networks subject to physical partitioning where
\processes can join, leave, or crash at any time. Adding a \process is
equivalent to add as many edges as necessary. Since adding an edge may
improve shortest paths, the protocol triggers a competition using
echos of Definition~\ref{def:fbplus}.  Removing a \process is
equivalent to removing all its edges. Removing an edge between two
\processes may invalidate the shortest path of one of involved
\processes plus downstream \processes, or impair the propagation of
staleness notifications. Therefore, the protocol reuses its detectors
of Lemma~\ref{lem:detector} to remove irrelevant messages from the
system.

### 2022-06-28 input/tablenotations.tex
major changes everywhere

\begin{table*}
  \scriptsize
  \centering
  \caption{\label{table:notations}Notation table.}
  \begin{tabularx}{\textwidth}{@{}lll@{}}
    \toprule
    Notation & Short & Description \\
    \midrule

    $G$ & \underline{G}raph    & Represents a network.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\

@@

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\

@@

    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\

    \bottomrule
  \end{tabularx}
\end{table*}

>>>>

% \begin{table*}
  \scriptsize
%  \centering
%  \caption{\label{table:notations}Notation table.}
  \begin{tabularx}{\textwidth}{@{}lll@{}}
    \toprule
    Notation & Short & Description \\
    \midrule

    $G$ & \underline{G}raph    & Represents a network.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
    $\pi_{xz}$/$\Pi_{xz}$  & \underline{p}ath/best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$/$|\Pi_{xz}|$ & sum of weights & Positive sum of weights of the path.\\

@@

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$/$r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node/\Process $x$.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. $d$, $s$, $r$ etc. are events.\\
    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\

@@

    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
    $\delta_x$   & source \underline{d}eletion & Message that notifies the possible deletion of Source $x$ by \Process $x$.\\
    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information.\\% since its broadcaster broadcast a newer message.\\

    \bottomrule
  \end{tabularx}
% \end{table*}
